Introduction to Causal Inference Models

### 2017-07-31 msm_introduction.Rmd
figured out how to reproduce table in naimi.

>>>>

Trying to replicate example in sas code.
```{r}
y_mod <- glm(Y ~ A1 + Z1 + A0 + A1*A0, data = td_sim_data, family = "gaussian")
z1_mod <- glm(Z1 ~ A0, data = td_sim_data, family = "binomial"(link="logit"))
a1_mod <- glm(A1 ~ Z1, data = td_sim_data, family = "binomial"(link="logit"))

# natural course estimate ----
nc_mu <- mean(predict(y_mod, newdata = td_sim_data, type = "response"))

# fully exposed ----
z1_pr <- mean(predict(z1_mod, newdata = mutate(td_sim_data, A0 = 1), type = "response"))
# simulate vector of new Z1 values accounting for prior A0
z1_vec <- ifelse(rbernoulli(n = nrow(td_sim_data), z1_pr)==T,1,0)

# update a1 
a1_pr <- mean(predict(a1_mod, newdata = mutate(td_sim_data, Z1 = z1_vec), 
                      type = "response"))
# simulate new a1 given z1 under a0 estimate
a1_vec <- ifelse(rbernoulli(n = nrow(td_sim_data), a1_pr)==T,1,0)
# update predicted Y where everyone is exposed at time 0 and 1, and accounting for Z1 | A0 =1 
all_exposed <- mean(predict(y_mod, newdata = mutate(td_sim_data, A1 = 1, A0 = 1, Z1 = z1_vec),
                type = "response"))
all_exposed

# unexposed
z1_pr <- mean(predict(z1_mod, newdata = mutate(td_sim_data, A0 = 0), type = "response"))
z1_vec <- ifelse(rbernoulli(n = nrow(td_sim_data), z1_pr)==T,1,0)
all_unexposed <- mean(predict(y_mod, newdata = mutate(td_sim_data, A1 = 0, A0 = 0, Z1 = z1_vec),
                type = "response"))
all_unexposed
# diff
all_exposed - all_unexposed

```
